### 2019-11-01 Action letter.Rmd
Add DSEM results and update action letter

We have addressed each of these issues in our detailed responses to the Reviewers below. Here, we provide an overview of changes made:

@@

This is indeed a misunderstanding, and we apologize for the lack of clarity. Please see our response to Reviewer 2, comment 8.

@@

We thank the Editor for pointing out the lack of consistency across sections, and we have edited the revised manuscript to resolve this issue. We now consistently use the terms "joint and relative quantitative involvement". Joint quantitative involvement is defined as the average involvement of two parents. Relative involvement is defined as the difference between mothers and fathers (not a ratio). These variables are obtained by re-expressing the variance of the two observed variables, absolute maternal and paternal involvement, into two latent variables, reflecting the mean difference. We have included a visual representation of the model, which should clarify this technique.

@@

@@

@@

@@

@@

@@

We agree wholeheartedly with this point, but there is a challenge: Because nobody has previously modeled the interplay between parental involvement and emotional adjustment in the way we have, controlling for stable between-family differences, and examining quantitative involvement in terms of the joint and relative contribution of mothers and fathers, there is no precedent upon which to base such hypotheses. Therefore, the best we can do is to present *conceptual* hypotheses.

@@

Median household income in Australia was $\$58708$ in 2006, the first year of data collection. We only have information on income categories, but in our sample, most families were dual earners, with most fathers reporting between \$26,000-\$51,999, and most mothers reporting \$25,999 of income. This seems to be very comfortably around the median income in Australia at the time. That makes sense, because the study contains a representative sample. We did decide to focus only on white urbanized Australians, because the amount of heterogeneity introduced by including rural and nonwhite/aboriginal Australians led to model non-convergence.

@@

All of this information requested is provided Supplementary Table 1, as stated in the text (*Scale descriptive statistics are provided in Supplementary Table 1*). Perhaps these supplementary Tables are not automatically shared with reviewers?

@@

This information is provided in the Measures section, as it should be:

@@

Several working papers have been written on the recruitment, participants, data collection, etc. for this sample. However, this information was masked in the original manuscript, to facilitate blind peer review. We feel that it is unnecessary to reproduce this information for a well-documented large cohort study, as we can simply cite the original material. However, as we also understand that the Reviewer needs access to these references to evaluate the study quality, we have now revealed the masked sections:

@@

Results

@@

@@

@@

This is explained in the strategy of analyses:

@@

@@

We do currently show the results in the form of Tables, but we have also included conceptual Figures to further clarify the model.

>>>>

We have addressed these four issues in our detailed responses to the Reviewers below. Here, we provide an overview of changes made:

@@

This is indeed a misunderstanding, and we apologize for the lack of clarity. Please see our response to Reviewer 2, comment 8. In this part of the Discussion section, we relate our findings to those of a previous study with a similar design.

@@

We thank the Editor for pointing out the lack of consistency across sections, and we have edited the revised manuscript to resolve this issue. We now consistently use the terms "joint and relative quantitative involvement". Joint quantitative involvement is defined as the average involvement of both parents (a latent mean). Relative involvement is defined as the difference between mothers and fathers (not a ratio; a latent difference). These variables are obtained by re-expressing the variance of the two observed variables, absolute amount maternal and paternal involvement, into two latent variables, reflecting the mean and difference. We have included a Figure that presents the model visually, which should clarify this technique. We also explicitly point out, once in the Introduction and once in the Discussion, that joint involvement represents the total amount of care provided to children, whereas relative involvement captures the childcare distribution who does what).

@@

We have elaborated on the Table notes. We think that the definition of joint and relative involvement is adequately addressed by the increased consistency with regard to terminology, in conjunction with the new Figure - but we are happy to take further action if necessary.

@@

To address this comment, we've attempted to ensure that every issue in the Introduction is paralleled in the Discussion. We have also attempted to clarify the between/within distinction. A major contribution of the present study is that we are (one of?) the first to make this distinction in this particular research area. Consequently, there is no prior literature available to base specific hypotheses about between/within effects on. The best we can do is develop exploratory hypotheses based on a conflicting literature that has lumped together between/within effects. Thus, we cannot make more specific predictions than we currently do.

@@

We appreciate this suggestion. We agree that parent effects could very well be present at even younger ages, and explicitly acknowledge this in the revision. At the same time, we think that it is interesting and potentially meaningful that parent effects - but not child effects - tend to become smaller/non significant when stable between-family differences are accounted for. We have attempted to clarify our discussion of the potential theoretical/methodological implications of this finding.

> Nowadays, it is commonly acknowledged that parents and children reciprocally influence one another. However, the methods used to demonstrate bi-directional effects have been criticized for misrepresenting the direction of effects when stable between-family differences are not accounted for [@hamakerCritiqueCrosslaggedPanel2015]. We are aware of only one prior study that controlled for stable between-family differences when examining the interplay between parenting and emotional adjustment. This study found that child effects substantially outnumbered parenting effects in adolescence [@vanlissaRoleFathersMothers2018a]. The authors explained this finding in light of the relative equality of parent-adolescent relationships. The present study casts doubt on that interpretation, as we found a preponderance of child effects between the ages of 6-12. Although it is, of course, possible that parent effects are in effect at an even younger age, we can also consider the question: To what extent are parents shaping children's development, and to what extent are they adapting to it?  
The finding that parent effects become smaller or non-significant once stable between-family differences are accounted for has also been demonstrated in other areas of developmental research (REF). As similar patterns continue to emerge, it might be worth reflecting on their implications for developmental theory. Such findings are less congruent with a fully bidirectional conceptualization of reciprocal influence, and more consistent with a model where parents "set the stage" for children's development through their stable differences from other parents, and continue to adjust to children's changing needs over time. Methodological innovations that examine the role of stable between-family differences can thus inspire more sophisticated theoretical conceptualizations of parental influences in child development.  
At the same time, we should consider the limitations of these methods. The assumption that within-family fluctuations adequately capture all causal influences that parents exert on their children, for instance, is questionable. Stable factors can also exert changing influences over time. As an illustrative example: The genetic makeup that is passed from parents to children is stable, and yet the expression of some genes emerges over time. It might similarly be possible for stable parental psychosocial characteristics to influence children differently at different time points. Another important limitation is that within-family cross-lagged effects are time scale dependent. If parents shape their children through specific behaviors in dyadic interactions, then annual reflective self-reports might fail to capture parenting effects. Thus, although these methodological innovations are undoubtedly a step forward, they might not be the definitive paradigm for investigating the interplay between parents and children.

@@

We agree, and as we mention in the manuscript, we also find these between-family differences in parents' responses to childen's emotional adjustment in the present study. In the rewritten paragraphs above, we have attempted to clarify that we are not making any claims about genes, but instead, we are questioning the assumption of the RI-CLPM model that all reciprocal influences are captured by within-family fluctuation. We then introduce genes as an illustrative example of something very stable that can nonetheless have changing influences over the life course. In the revision, we have emphasized that this is an illustrative example, and we then draw a parallel to how stable psychosocial traits might similarly have changing effects over the course of development.

@@

Thank you for pointing out that sex differences are omitted from the list of contributions mentioned in *The Present Study*. We have attempted to address this issue by adding sex differences to the list, and we have also clarified our specific hypotheses regarding sex differences in the preceding paragraph.

> We therefore hypothesize that parents will display more responsiveness, structure, and inductive reasoning towards girls, and more negative parenting towards boys. Furthermore, we predict stronger associations between qualitative parenting and emotional adjustment between children and the same-sex parent.  
*[...]*
Consequently, we have no hypothesis regarding sex differences in children's average levels of emotional adjustment.  
*[...]*
Finally, we examined sex as a moderator of between-family differences in all study variables and within-family predictive effects

@@

We agree wholeheartedly with this point, and we had formulated hypotheses for all patterns studied, but we understand that our colloquial use of language made it hard to identify our specific hypotheses. For example, in the original manuscript, we wrote:

> Applying this insight from the coparenting literature, we might thus expect parents' quantitative involvement to be directly associated with their qualitative parenting behaviors and children's emotional adjustment, and to moderate effects between qualitative parenting behaviors and emotional adjustment.

In the revision, we have attempted to address this comment by being more specific. Now, this section reads:

> Applying this insight from the coparenting literature, we thus hypothesize that  parents' quantitative involvement will be directly associated with their qualitative parenting behaviors and children's emotional adjustment, and will moderate effects between qualitative parenting behaviors and emotional adjustment.

There is a bit of a challenge, however: Because there is no precedent for using the random-intercept cross-lagged panel model or its multilevel DSEM extension in the literature on parental involvement and emotional adjustment, there is no literature upon which to base such hypotheses. Therefore, the best we can do is to present *conceptual* hypotheses.

@@

Median household income in Australia was $\$58.708$ in 2006, the first year of data collection. We only have information on income categories, but in our sample, most families were dual earners, with most fathers reporting between \$26,000-\$51,999, and most mothers reporting \$25,999 of income. This seems to be very close to the median income in Australia at the time. That makes sense, because the study contains a representative sample. We did decide to select only white urbanized Australians from that sample, because initial exploratory analyses indicated that the amount of heterogeneity introduced by including rural and nonwhite/aboriginal Australians led to model non-convergence.

@@

This might be an oversight, as all of this information requested is provided in Supplementary Table 1 (*Scale descriptive statistics are provided in Supplementary Table 1*). Perhaps these supplementary Tables are not automatically shared with reviewers?

@@

This information is provided in the Measures section:

@@

Several working papers have been written on the recruitment, participants, data collection, etc. for this sample. However, this information was masked in the original manuscript, to enable blind peer review. However, as both Reviewers and the Editor requested access to these references to evaluate the study quality, we have now unmasked these sections in the revised manuscript:

@@

@@

*Probably, we should cite the values in the text, as the Editor also suggested.*

@@

We have attempted to address this comment by labeling and annotating the Tables more extensively.

@@

In the original manuscript, we explained how sex differences were tested in the strategy of analyses:

@@

In the revision, we have attempted to further clarify this by including a visual representation of the model, and by labeling Tables more clearly.

@@

In the original manuscript, we included four Tables with the results reported in the Results section. In the revision, we have additionally included a Figure to further clarify the model.
